Supplementary Material

### 2021-04-22 paper/ifo-supplementary-material.tex
work in progress on supp mat

\section{Optical microphone signal processing}
\han{Notes - I've just made a start at moving material over. We will need to go through once we make final decisions on what to show in the main text / when new figures ready to check things}

@@

In Section~V of the main article, we use the interferometer as an optical microphone. Photographs of the physical apparatus of the optical microphone are shown in Fig.~\ref{fig:photographs_of_optical_microphone_and_circuit}.
We use signal processing techniques to recover audio signals of speech and music. 
In this supplementary material we provide further details of a selection of analysis applied to the data which may be considered for undergraduate laboratory examples.  
We start with some na{\"i}ve approaches and then move to traditional signal processing filters (band-passing and cascaded notches). 
We finish by combining these with advanced statistical techniques (Wiener filter and the logMMSE estimator). 
As an illustrative example, we test all of these filters on the same $1\,{\rm s}$ long speech recording.

\begin{figure*}
	\begin{center}
    %% trim order is <left> <lower> <right> <upper>
    % height=0.5\textheight,trim={1cm 4.5cm 0.4cm 3.5cm},clip
	\includegraphics[width=.8\textwidth, trim={1cm 3cm 1cm 1cm}]{figures/notch_and_wiener_superplot_v2.pdf}
	\end{center}
	\caption{\label{fig:BackgroundNotchWienerCombined}
	\jam{Fig.2 should be combined with Fig.6 using combined\_results\_full\_melatos\_labelled.pdf}
	Timeseries (left column) and frequency spectrum (right column) results for the background subtraction, notch, and Wiener filters.
    The source signal, shown in the first row, is a $1\,{\rm s}$ recording of an adult male voice (saying ``A cathode ...''). 
    The source signal is shifted by $0.12\,{\rm s}$ to the right to synchronise the manual delay from starting the recording with the Raspberry Pi and starting to play the source through the speaker. 
	The second row shows the raw output from the optical microphone when the input signal from the first row is played. 
    The third row shows a background noise recording from the optical microphone when no audio signal is played. 
    The fourth row shows the result of subtracting the background noise spectrum in the third row from the recording in the second row. 
	The fifth, sixth, and seventh rows show the results of applying the notch filter, the Wiener filter, and both combined, respectively.
	}
\end{figure*}

Results for a selection of filters are collated in Fig.~\ref{fig:BackgroundNotchWienerCombined} where the left and right columns show timeseries and Fourier spectrum results, respectively. 
The first and second rows of Fig.~\ref{fig:BackgroundNotchWienerCombined} show the source signal and the raw optical microphone recording, respectively. 
The third row shows a background spectrum of the optical microphone. 
The following sections describe each of the analysis in turn.

@@

Given that we have access to the background noise spectrum, an intuitive way to remove noise is via subtracting the noise spectrum from the recorded spectrum. 
The fourth row of Fig.~\ref{fig:BackgroundNotchWienerCombined} shows the spectrum obtained after subtracting the background noise spectrum. 
We see no obvious improvement, which may be attributed to a time-variant noise spectrum, the cause of which is unidentified.

@@

We use the built-in MATLAB filter design toolbox in this work~\cite{MATLAB}. 
The amplitude (magnitude) response of the first five notch filters is shown in Fig.~\ref{fig:notchMagResponse}. 
The time series and spectrum obtained after applying the cascade notch filter to the speech recording are shown in the fifth row of Fig.~\ref{fig:BackgroundNotchWienerCombined}.
We see that the mains harmonics are significantly attenuated in comparison background subtracted results shown in the fourth row of Fig.~\ref{fig:BackgroundNotchWienerCombined}.

@@

In this work, we construct a higher-order causal Wiener filter based on Eqn.~\ref{eqn:wiener-hopf}. A higher-order Wiener filter provides greater smoothing of the input signal but also increases the computational memory required. For this work, we choose a Wiener filter of order $n=100$ as it provides a reasonable balance between smoothing and efficiency. The timeseries and frequency spectrum after applying the Wiener filter are shown in the sixth row of Fig.~\ref{fig:BackgroundNotchWienerCombined}.
We see a significant improvement in the timeseries of the recovered signal, however, a strong noise hum persists, audibly.

@@

By combining the notch and Wiener filter, we can trade-off between the two and achieve an overall better performance, as can be seen in the bottom row of Fig.~\ref{fig:BackgroundNotchWienerCombined}.
The filtered voice after the combined notch and Wiener filter is enhanced compared to either alone. The mains noise is all but removed and more voice information is retained. However, the recovered voice still sounds muffled and is not understandable.

>>>>

\section{Optical microphone signal processing}

In Section~V in the main article, we use the interferometer as an optical microphone; audio signals are used to vibrate the interferometer mirrors and the signals are recovered from a timeseries of the interference pattern changing.
In this Supplementary Material we include a selection of signal processing techniques applied to the data which may be considered for undergraduate laboratory examples. 
We start with some na{\"i}ve approaches and then move to traditional signal processing filters (band-passing and cascaded notches). 
We finish by combining these with advanced statistical techniques (Wiener filter and the logMMSE estimator). 
As an illustrative example, we test all of these filters on the same $1\,{\rm s}$ long speech recording.

@@

All analysis is done using the photodiode set-up as described in Section~V.A. of the main text. 
A photograph of the equipment is shown in Fig.~\ref{fig:photographs_of_optical_microphone_and_circuit} with the interferometer and circuit shown on the left and right respectively.

\begin{figure}
	\begin{center}
    %% trim order is <left> <lower> <right> <upper>
    % height=0.5\textheight,trim={1cm 4.5cm 0.4cm 3.5cm},clip
	\includegraphics[width=.5\textwidth]
% trim={1cm 3cm 1cm 1cm}]
{figures/combined_results_full_melatos_labelled.pdf}
%notch_and_wiener_superplot_v2.pdf}
	\end{center}
	\caption{\label{fig:op_mic_results}
	\jam{Fig.2 should be combined with Fig.6 using combined\_results\_full\_melatos\_labelled.pdf}
	Timeseries (left column) and frequency spectrum (right column) results for the background subtraction, notch, and Wiener filters.
    The source signal, shown in the first row, is a $1\,{\rm s}$ recording of an adult male voice (saying ``A cathode ...''). 
    The source signal is shifted by $0.12\,{\rm s}$ to the right to synchronise the manual delay from starting the recording with the Raspberry Pi and starting to play the source through the speaker. 
	The second row shows the raw output from the optical microphone when the input signal from the first row is played. 
    The third row shows a background noise recording from the optical microphone when no audio signal is played. 
    The fourth row shows the result of subtracting the background noise spectrum in the third row from the recording in the second row. 
	The fifth, sixth, and seventh rows show the results of applying the notch filter, the Wiener filter, and both combined, respectively.
	}
\end{figure}

Results for a selection of filters are collated in Fig.~\ref{fig:op_mic_results}, which re refer to throughout the text. 
The left and right columns show timeseries and Fourier spectrum results, respectively. 
The first and second rows of Fig.~\ref{fig:op_mic_results} show the source signal and the raw optical microphone recording, respectively. 
The third row shows a background spectrum of the optical microphone. 
The following sections describe each of the analysis in turn.

@@

An inituitive way to remove noise is by directly subtracting the background noise (third row of Fig.~\ref{fig:op_mic_results}) from the recorded spectrum. 
The fourth row of Fig.~\ref{fig:op_mic_results} shows the spectrum obtained after subtracting the background noise spectrum. 
We see no obvious improvement, which may be attributed to a time-variant noise spectrum, the cause of which is unidentified.

@@

We use the built-in MATLAB filter design toolbox in this work~\cite{MATLAB}. 
The amplitude (magnitude) response of the first five notch filters is shown in Fig.~\ref{fig:notchMagResponse}. 
The time series and spectrum obtained after applying the cascade notch filter to the speech recording are shown in the fifth row of Fig.~\ref{fig:op_mic_results}.
We see that the mains harmonics are significantly attenuated in comparison background subtracted results shown in the fourth row of Fig.~\ref{fig:op_mic_results}.

@@

In this work, we construct a higher-order causal Wiener filter based on Eqn.~\ref{eqn:wiener-hopf}. A higher-order Wiener filter provides greater smoothing of the input signal but also increases the computational memory required. For this work, we choose a Wiener filter of order $n=100$ as it provides a reasonable balance between smoothing and efficiency. The timeseries and frequency spectrum after applying the Wiener filter are shown in the sixth row of Fig.~\ref{fig:op_mic_results}.
We see a significant improvement in the timeseries of the recovered signal, however, a strong noise hum persists, audibly.

@@

By combining the notch and Wiener filter, we can trade-off between the two and achieve an overall better performance, as can be seen in the bottom row of Fig.~\ref{fig:op_mic_results}.
The filtered voice after the combined notch and Wiener filter is enhanced compared to either alone. The mains noise is all but removed and more voice information is retained. However, the recovered voice still sounds muffled and is not understandable.
